---
title: "Car Finder Application"
author: "Rana El-Robi"
date: "February 15, 2018"
output:
  slidy_presentation: default
  ioslides_presentation:
    template: Car-Finder-Application.html
---
# About App
  
- Car Finder is user fiendly [App](https://rana-elrobi.shinyapps.io/Car-Finder-App/), in which:
  - It has many option to fit your needs, like : 
  - Car Type (Manual/Automatic)
  - Number of cylinders
  - Displacment
  - Distance covered in miles
  - Estimated gasoline price
  
Also,

- Its is supported with very nice [User Manual](https://github.com/Rana-ElRobi/Project-Shiny-Application-and-Reproducible-Pitch/blob/master/App-Documentation.md) with screen shots for the app
- Full [code](https://github.com/Rana-ElRobi/Project-Shiny-Application-and-Reproducible-Pitch/tree/master/FinalshinyApp)

---

## About Data Used
- Dataset used called `mtcars`
```{r}
head(mtcars[,1:5],8)
```
> Note : This custmization in `head()` is for better representation

---

## Sampel of code with default values 
```{r}
library(dplyr)
disp_seq <- seq(from = 160, to = 325, by = 0.1) 
reshaped.data <- transmute(mtcars,Car = rownames(mtcars),MilesPerGallon = mpg,GasolineExpenditure = 30/mpg*3.2, Cylinders = 8,Displacement = 160, Transmission = 0) 
filtered.data <- filter(reshaped.data , Cylinders %in% c(4,8),Displacement %in%disp_seq,Transmission %in% 0)
labelled.data <- mutate(filtered.data,Transmission = ifelse(Transmission==0,"Automatic","Manual"))
resultant.data <- arrange(labelled.data, GasolineExpenditure) 
```

---
## Filtered Results

After Calculations and filtering data, Results will be like this
```{r}
colnames(resultant.data) <- c("car","miles","gas" ,"cly","Disp","Type")
head(resultant.data,10) 
```

